CS246: Twitter Purification

### 2014-06-08 Paper.tex
Edits

\paragraph{} Two analysis passes of a potentially malformed tweets are used: once for single word correction, and the second for contextual analysis. For single word correction, we use a combination of common abbreviations, word frequency, dictionary presence, and distance between a potential correction candidate and the original word. Distance is defined in terms of edit distance, phonetic class, and overall letter similarity. Contextual analysis uses bigram frequency to find the best candidate in cases where single word correction still left ambiguity.

@@

\paragraph{} Approximately 800,000 tweets consisting of about 120,000 distinct words were harvested Twitter's sample API\footnote{\href{https://dev.twitter.com/docs/api/1.1/get/statuses/sample}{GET statuses/sample}}. Word tokens were defined as any whitespace delimited string that begins with an alphabet letter and otherwise may include alphanumeric characters, apostrophes, or hyphens. We excluded some Twitter specific tokens, including usernames (strings that begin with @), hashtags (strings that begin with \#), emoticons, and internet urls (\textit{http(s)://...}). All strings were converted to lowercase for analysis. Final corrected output replaced any usernames with ]\textit{username}], and a hardcoded list of laughter tokens were converted to [\textit{laughter}].\footnote{lmao, lmfao, lolz, lol, rofl, lls, haha}

@@

\paragraph{} In the case where a word is encountered that does not exist in a dictionary, it is often more appropriate to not apply a correction. Slang and proper nouns abound in Twitter; while the line between a legitimate word versus a misspelling can be blurry, e.g. \textit{want to} vs \textit{wanna}, but a great deal of slang have no `correct' equivalent in a dictionary, e.g. Twitter specific words such as \textit{retweet} as well as many more vulgar examples.
\paragraph{}Nonetheless, a high quality dictionary was desirable for this project. Word candidates that exist in the dictionary can therefore be weighted more heavily, and correctly spelled obscure words can avoid being overwhelmed by exceptionally common words that are closely phonetically related or via edit distance (e.g. \textit{goat} being overwhelmed by the frequency of \textit{got}. Initially, a union of UNIX's dictionary, Google Translate's list of most frequently used words\footnote{\href{https://github.com/first20hours/google-10000-english}{google-10000-english}}, and the most common words from TV and movie scripts\footnote{\href{http://en.wiktionary.org/wiki/Wiktionary:Frequency_lists\#TV_and_movie_scripts}{Wiktionary Frequency Lists}} was used. However, this failed to produce an acceptable dictionary, partially due to the overinclusion of slang and underinclusion of conjugated verbs or plurals. Inevitably, we settled upon using Ispell's english dictionary, which consisted of 143,006 words.\footnote{\href{http://fmg-www.cs.ucla.edu/geoff/ispell-dictionaries.html}{Dictionaries for International Ispell}}
\paragraph{} In the context of Twitter purification, if the given word exists in the dictionary, it is guaranteed a position in the final list of correction candidates, with the same weight as that of the frontrunner candidate (if different). Furthermore, any candidates that exist in the dictionary are weighted more heavily by $+20\%$.

@@

\subsection*{Single word results}

@@

\subsection*{Bigram results}

@@

\lstset{basicstyle=\footnotesize\ttfamily, 
	tabsize=2,
	language=Python,
	backgroundcolor=\color{lightgray},
	commentstyle=\color{mygreen},
	keywordstyle=\color{blue},
	stringstyle=\color{red}\ttfamily,
	showstringspaces=false,
	breaklines=true
}
\end{document}

>>>>

\paragraph{} Two analysis passes of potentially malformed tweets are used: once for single word correction, and the second for contextual analysis. For single word correction, we use a combination of common abbreviations, word frequency, dictionary presence, and distance between a potential correction candidate and the original word. Distance is defined in terms of edit distance, phonetic class, and overall letter similarity. Contextual analysis uses bigram frequency to find the best candidate in cases where single word correction still left ambiguity.

@@

\paragraph{} Approximately 800,000 tweets consisting of about 120,000 distinct words were harvested via Twitter's sample API\footnote{\href{https://dev.twitter.com/docs/api/1.1/get/statuses/sample}{GET statuses/sample}}. Word tokens were defined as any whitespace delimited string that begins with an alphabet letter and otherwise may include alphanumeric characters, apostrophes, or hyphens. We excluded some Twitter specific tokens, including usernames (strings that begin with @), hashtags (strings that begin with \#), emoticons, and internet urls (\textit{http(s)://...}). All strings were converted to lowercase for analysis. Final corrected output replaced any usernames with [\textit{username}], and a hardcoded list of laughter tokens were converted to [\textit{laughter}].\footnote{lmao, lmfao, lolz, lol, rofl, lls, haha}

@@

\paragraph{} In the case where a word is encountered that does not exist in a dictionary, it is often more appropriate to not apply a correction. Slang and proper nouns abound in Twitter; while the line between a legitimate word versus a misspelling can be blurry, e.g. \textit{want to} vs \textit{wanna}, a great deal of slang have no `correct' equivalent in a dictionary, e.g. Twitter specific words such as \textit{retweet} as well as many more vulgar examples.
\paragraph{}Nonetheless, a high quality dictionary was desirable for this project. Word candidates that exist in the dictionary can therefore be weighted more heavily, and correctly spelled obscure words can avoid being overwhelmed by exceptionally common words that are closely phonetically related or via edit distance (e.g. \textit{goat} being overwhelmed by the frequency of \textit{got}). Initially, a union of UNIX's dictionary, Google Translate's list of most frequently used words\footnote{\href{https://github.com/first20hours/google-10000-english}{google-10000-english}}, and the most common words from TV and movie scripts\footnote{\href{http://en.wiktionary.org/wiki/Wiktionary:Frequency_lists\#TV_and_movie_scripts}{Wiktionary Frequency Lists}} was used. However, this failed to produce an acceptable dictionary, partially due to the overinclusion of slang and underinclusion of conjugated verbs or plurals. Inevitably, we settled upon using Ispell's english dictionary, which consists of 143,006 words.\footnote{\href{http://fmg-www.cs.ucla.edu/geoff/ispell-dictionaries.html}{Dictionaries for International Ispell}}
\paragraph{} In the context of Twitter purification, if the given word exists in the dictionary, it is guaranteed a position in the final list of correction candidates, with the same weight as that of the front-runner candidate. Furthermore, any candidates that exist in the dictionary are weighted more heavily by $+20\%$.

@@

@@

@@

\lstset{basicstyle=\footnotesize\ttfamily, 
	tabsize=2,
	language=Python,
	backgroundcolor=\color{lightgray},
	commentstyle=\color{mygreen},
	keywordstyle=\color{blue},
	stringstyle=\color{red}\ttfamily,
	showstringspaces=false,
	breaklines=true
}

\section*{References}

\end{document}
